Changes to police demand in COVID-19 pandemic

### 2022-05-04 docs/index.Rmd
presentation for Loreen students

---
title: "Changes to police demand in COVID-19 pandemic"
subtitle: "N8PRP Webinar"
author: "Réka Solymosi, Matt Ashby, Eon Kim, Nadia Kennar, Karen Byrom, Alex McMillan, Phoebe Liebelt"
institute: "University of Manchester, Cheshire Constabulary, UCL"
date: "24/03/2022"
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---
class: center, middle

@@

@@

@@

---
class: center, middle
# Sharing the learning

- [UKDS webinar: an introduction to time series analysis and forecasting](https://ukdataservice.ac.uk/events/an-introduction-to-time-series-analysis-and-forecasting-2/)
- A co-developed series for analysts using R and Python

>>>>

---
title: "Changes to police demand in COVID-19 pandemic"
subtitle: ""
author: "Réka Solymosi, Matt Ashby, Eon Kim, Nadia Kennar, Karen Byrom, Alex McMillan, Phoebe Liebelt"
institute: "University of Manchester, Cheshire Constabulary, UCL"
date: "10/05/2022"
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---
class: center, middle

@@

# Quiet roads

```{r quietroadsplots, fig.width=11,fig.height=8}

p1 <- forecast_chart(call_forecasts, "incident_type_new" ,"traffic collision") + 
  labs(title = "Traffic Collision",
      subtitle = "",
      caption = "",
      x = NULL,
      y = NULL,
      fill = NULL) + 
  guides(fill="none")
p2 <- forecast_chart(call_forecasts, "incident_type_new" ,"Highway Disruption")+ 
  labs(subtitle = "", caption = "", x = NULL, fill = NULL) + 
  guides(fill="none")
p3 <- forecast_chart(call_forecasts, "incident_type_new" ,"Road Related Traffic Offence")  +
  labs(subtitle = "",
      caption = "Forecast calculated using data up to 31 January 2020",
      x = NULL,
      y = NULL,
      fill = "Actual observed value significantly different from forecast")

gridExtra::grid.arrange(p1, p2, p3, ncol = 1)

@@

# Presence of guardians/ absence of targets

```{r guardiansplot1, fig.width=11,fig.height=8}

forecast_chart(call_forecasts, "incident_type_new", "Burglary - Residential")

# Presence of guardians/ absence of targets

```{r guardiansplot2, fig.width=11,fig.height=7}

p1 <- forecast_chart(call_forecasts, "incident_type_new", "Theft From Motor Vehicle") + 
  labs(subtitle = "", caption = "", x = NULL, y = NULL, fill = NULL) + 
  guides(fill="none")
p2 <- forecast_chart(call_forecasts, "incident_type_new", "Theft Of Motor Vehicle") + 
  labs(subtitle = "", caption = "", x = NULL, y = NULL, fill = NULL) + 
  guides(fill="none")
p3 <- forecast_chart(call_forecasts, "incident_type_new", "Theft Other")

gridExtra::grid.arrange(p1, p2,p3, ncol = 1)

# Presence of guardians/ absence of targets

```{r guardiansplot3, fig.width=11,fig.height=7}

p1 <- forecast_chart(call_forecasts, "incident_type_new", "Shoplifting") + 
  labs(subtitle = "", caption = "", x = NULL, y = NULL, fill = NULL) + 
  guides(fill="none")
p2 <- forecast_chart(call_forecasts, "incident_type_new", "Robbery")

gridExtra::grid.arrange(p1, p2, ncol = 1)

```
---

# Police response: Attendance rate

```{r allattendedfig, fig.width=11,fig.height=7}

# % attended fig and response time fig
all_calls_attended_forecast %>% 
    mutate(forecast_lower = ifelse(forecast_lower < 0, 0, forecast_lower)) %>% 
    ggplot() +
    # Forecast
    geom_ribbon(
      aes(incident_week, ymin = forecast_lower, ymax = forecast_upper), 
      na.rm = TRUE,
      alpha = 0.5, 
      fill = "grey80"
    ) +
    geom_line(aes(incident_week, forecast_mean), na.rm = TRUE, linetype = "22") +
    # Dates of interest
    geom_vline(aes(xintercept = date), data = dates, linetype = "12") +
    geom_label(aes(date, 0, label = row), data = dates, colour = "grey20") +
    # Actual calls
    geom_line(aes(incident_week, actual_attended)) +
    geom_point(aes(incident_week, actual_attended, fill = sig), shape = 21) +
    scale_x_date(date_labels = "%e %b\n%Y", 
               limits = as.Date(c("2020-01-06", "2020-12-21"))) +
    scale_y_continuous(limits = c(0, NA), labels = scales::comma_format()) +
    scale_fill_manual(values = c(`TRUE` = "black", `FALSE` = "grey80")) +
    labs(
      title = "Attendance rate for all calls for service during 2020 compared to pre-pandemic forecast",
      subtitle = str_wrap(
        str_glue("Events by week: ", str_c(pull(dates, label), collapse = "; ")), 
        80
      ),
      caption = "Forecast calculated using data up to 31 January 2020",
      x = NULL,
      y = "weekly % of calls attended",
      fill = "actual % significantly different from forecast"
    ) +
    theme_minimal() +
    theme(legend.position = "bottom", plot.title = element_text(face = "bold"))

# Police response: Attendance rate

```{r bygradeattendedperc, fig.width=11,fig.height=7}

p1 <- forecast_chart(attended_by_grade_forecast,"initial_grade_of_response", "Grade 1") + 
  labs(subtitle = "", caption = "", x = NULL, fill = NULL) + 
  guides(fill="none")
p2 <- forecast_chart(attended_by_grade_forecast,"initial_grade_of_response", "Grade 2") + 
  labs(subtitle = "", caption = "", x = NULL, y = NULL, fill = NULL) + 
  guides(fill="none")
p3 <- forecast_chart(attended_by_grade_forecast,"initial_grade_of_response", "Grade 3") + 
  labs(subtitle = "", caption = "", x = NULL, y = NULL, fill = NULL) + 
  guides(fill="none")
p4 <- forecast_chart(attended_by_grade_forecast,"initial_grade_of_response", "Grade 4") + 
  labs(subtitle = "", caption = "", x = NULL, y = NULL, fill = NULL) + 
  guides(fill="none")

gridExtra::grid.arrange(p1, p2, p3, p4, ncol = 2)

# Police response: Response time

```{r allresptimefig, fig.width=11,fig.height=8}

all_rt_forecast %>% 
    mutate(forecast_lower = ifelse(forecast_lower < 0, 0, forecast_lower)) %>% 
    ggplot() +
    # Forecast
    geom_ribbon(
      aes(incident_week, ymin = forecast_lower, ymax = forecast_upper), 
      na.rm = TRUE,
      alpha = 0.5, 
      fill = "grey80"
    ) +
    geom_line(aes(incident_week, forecast_mean), na.rm = TRUE, linetype = "22") +
    # Dates of interest
    geom_vline(aes(xintercept = date), data = dates, linetype = "12") +
    geom_label(aes(date, 0, label = row), data = dates, colour = "grey20") +
    # Actual calls
    geom_line(aes(incident_week, actual_rt)) +
    geom_point(aes(incident_week, actual_rt, fill = sig), shape = 21) +
    scale_x_date(date_labels = "%e %b\n%Y") +
    scale_y_continuous(limits = c(0, NA), labels = scales::comma_format()) +
    scale_fill_manual(values = c(`TRUE` = "black", `FALSE` = "grey80")) +
    labs(
      title = "Median response time for all calls for service during 2020 compared to pre-pandemic forecast",
      caption = "Forecast calculated using data up to 31 January 2020",
      x = NULL,
      y = "Median response time in minutes",
      fill = "Response time significantly different from forecast"
    ) +
    theme_minimal() +
    theme(legend.position = "bottom", plot.title = element_text(face = "bold"))

# Police response: Response time

```{r bygraderesptime, fig.width=11,fig.height=7}

p1 <- forecast_chart(by_grade_rt_forecast,"initial_grade_of_response", "Grade 1") + 
  labs(subtitle = "", caption = "", x = NULL, fill = NULL) + 
  guides(fill="none")
p2 <- forecast_chart(by_grade_rt_forecast,"initial_grade_of_response", "Grade 2") + 
  labs(subtitle = "", caption = "", x = NULL, y = NULL, fill = NULL) + 
  guides(fill="none")
p3 <- forecast_chart(by_grade_rt_forecast,"initial_grade_of_response", "Grade 3") + 
  labs(subtitle = "", caption = "", x = NULL, y = NULL, fill = NULL) + 
  guides(fill="none")
p4 <- forecast_chart(by_grade_rt_forecast,"initial_grade_of_response", "Grade 4") + 
  labs(subtitle = "", caption = "", x = NULL, y = NULL, fill = NULL) + 
  guides(fill="none")

gridExtra::grid.arrange(p1, p2, p3, p4, ncol = 2)

# Police response: Time on scene

Need alltogether time on scene graph here

# Police response: Time on scene

```{r bygradetos, fig.width=11,fig.height=7}

p1 <- forecast_chart(by_grade_tos_forecasts,"initial_grade_of_response", "Grade 1") + 
  labs(subtitle = "", caption = "", x = NULL, fill = NULL) + 
  guides(fill="none")
p2 <- forecast_chart(by_grade_tos_forecasts,"initial_grade_of_response", "Grade 2") + 
  labs(subtitle = "", caption = "", x = NULL, y = NULL, fill = NULL) + 
  guides(fill="none")
p3 <- forecast_chart(by_grade_tos_forecasts,"initial_grade_of_response", "Grade 3") + 
  labs(subtitle = "", caption = "", x = NULL, y = NULL, fill = NULL) + 
  guides(fill="none")
p4 <- forecast_chart(by_grade_tos_forecasts,"initial_grade_of_response", "Grade 4") + 
  labs(subtitle = "", caption = "", x = NULL, y = NULL, fill = NULL) + 
  guides(fill="none")

gridExtra::grid.arrange(p1, p2, p3, p4, ncol = 2)

@@
